{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-09-23 ident_manu.Rnw
updating results with new fishtank mod

<<echo = FALSE>>=
pars <- parcats2(as_df = TRUE)$shrt %>% 
  as.character
rmpars <- c('Kw_1', 'Kcdom_1', 'Kspm_1', 'Kchla_1', 'aw490_1', 'astarOMR_1', 'astarOMBC_1', 'KTg1(nospA+nospZ)_1', 'KTg1(nospA+nospZ)_2', 'KTg1(nospA+nospZ)_3', 'KTg1(nospA+nospZ)_4', 'KTg1(nospA+nospZ)_5', 'KTg1(nospA+nospZ)_6', 'KTg1(nospA+nospZ)_7', 'KTg1(nospA+nospZ)_8', 'KTg2(nospA+nospZ)_1', 'KTg2(nospA+nospZ)_2', 'KTg2(nospA+nospZ)_3', 'KTg2(nospA+nospZ)_4', 'KTg2(nospA+nospZ)_5', 'KTg2(nospA+nospZ)_6', 'KTg2(nospA+nospZ)_7', 'KTg2(nospA+nospZ)_8', 'Ea_R(nospA+nospZ)_1', 'Ea_R(nospA+nospZ)_2', 'Ea_R(nospA+nospZ)_3', 'Ea_R(nospA+nospZ)_4', 'Ea_R(nospA+nospZ)_5', 'Ea_R(nospA+nospZ)_6', 'Ea_R(nospA+nospZ)_7', 'Ea_R(nospA+nospZ)_8', 'beta_1', 'beta_2', 'beta_3', 'beta_4', 'beta_5', 'beta_6', 'QmaxN_1', 'QmaxN_2', 'QmaxN_3', 'QmaxN_4', 'QmaxN_5', 'QmaxN_6', 'QmaxP_1', 'QmaxP_2', 'QmaxP_3', 'QmaxP_4', 'QmaxP_5', 'QmaxP_6', 'nfQs_1', 'nfQs_2', 'nfQs_3', 'nfQs_4', 'nfQs_5', 'nfQs_6', 'KG1_R_1', 'KG2_R_1', 'KG1_BC_1', 'KG2_BC_1', 'pCO2_1', 'stoich_x1R_1', 'stoich_y1R_1', 'stoich_x2R_1', 'stoich_y2R_1', 'stoich_x1BC_1', 'stoich_y1BC_1', 'stoich_x2BC_1', 'stoich_y2BC_1', 'sink OM1_R_1', 'sink OM2_R_1', 'sink OM1_BC_1', 'sink OM2_BC_1', 'CF_SPM_1')
rmpars <- c(rmpars, 'respb_7') # there's an extra of this one
pars <- pars[!pars %in% rmpars]
p1z1pars <- grep('_1$|_7$', pars, value = TRUE) # get parameters for one phyto, one zoop (_7 is for temp)

# number of parameters in each category
nparms <- parcats2(as_df = TRUE) %>% 
  filter(!shrt %in% rmpars) %>% 
  filter(grepl('_1$|_7$', shrt)) %>% 
  .$cats %>% 
  table %>% 
  as.list

@@

The effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.  These analyses used changes in parameter uncertainty and identifiability to infer the effects of observational and structural uncertainty on model output to create a more comprehensive evaluation.  First, observational uncertainty was evaluated by varying the initial conditions supplied to the model.  The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.  For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplnakton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.  Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.  Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.  Initial conditions were also changed to test the effects of different limiting nutrients by setting nitrogen and phosphorus values above or below concentrations defined by the standard Redfield ratio.

@@

% effects of structural uncertainty
<<streval, fig.cap = 'Effects of model structure on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
# structural
data(struct_eval)

>>>>

<<echo = FALSE>>=
p1z1pars <- par_tst()

# number of parameters in each category
nparms <- parcats2(as_df = TRUE) %>% 
  filter(shrt %in% p1z1pars) %>% 
  .$cats %>% 
  table %>% 
  as.list

@@

The effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.  These analyses used changes in parameter uncertainty and identifiability from results using the model's default configuration to infer the effects of observational and structural uncertainty on model output.  First, observational uncertainty was evaluated by varying the initial conditions supplied to the model.  The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.  For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplankton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.  Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.  Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.  Initial conditions were also changed to test the effects of different limiting nutrients by setting nitrogen and phosphorus values above or below concentrations defined by the standard Redfield ratio.

@@

% effects of structural uncertainty
<<streval, fig.cap = 'Effects of model structure on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = F, echo = F, warning = F, message = F>>=
# structural
data(struct_eval)
